
---
title: "2023 Pre-assessment workshop for black rockfish in waters off Washington state"
author: 
  - Jason M. Cope, Northwest Fisheries Science Center
  - Vladlena Gertseva, Northwest Fisheries Science Center
  - Fabio P. Caltabellotta, Washington Department of Fish and Wildlife
  - R. Claire Rosemond, Northwest Fisheries Science Center
  - Alison D. Whitman, Oregon Department of Fish and Wildlife
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
    fig_caption: yes
  #prettydoc::html_pretty:
    theme: bootstrap
    #highlight: tango

---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.pos = "!H",
  out.extra = "",
  collapse = TRUE,
  comment = "#>"
)

library(sa4ss)

dir <- "C:/Users/Jason.Cope/Documents/Github/Sebastes_melanops_WA/docs/Pre_assessment"

```

# 


**_Disclaimer: All data summaries and exploration presented here are preliminary and may not be indicative of the final data that will be incorporated in the 2025 assessment models_**


# Overview

Description of data and model specification being considered for use in the 2025 Rougheye and Blockspotted rockfishes assessment. Both of these species are treated as a rockfish complex, as they are difficult to visually separate, and thus most data are only avaibale as combined rougheye/blackspotted. 


```{r child = "1_summary_of_2021_assessment.Rmd"}
```


```{r child = "2_potential_model_fleet_structure.Rmd"}
```


```{r child = "3_removals.Rmd"}
```


```{r child = "4_indices.Rmd"}
```


```{r child = "5_composition_data.Rmd"}
```


```{r child = "6_biology.Rmd"}
```





