
---
title: "2025 Pre-assessment workshop for Rougheye and Blackspotted rockfishes in waters off the US West Coast"
author: 
  - Jason M. Cope, Northwest Fisheries Science Cente, jason.cope@noaa.gov
  - Vladlena Gertseva, Northwest Fisheries Science Center, vladlena.Gertseva@noaa.gov
  - R. Claire Rosemond, Northwest Fisheries Science Center, claire.rosemond@noaa.gov
  - Fabio P. Caltabellotta, Washington Department of Fish and Wildlife, Fabio.PriorCaltabellotta@dfw.wa.gov 
  - Alison D. Whitman, Oregon Department of Fish and Wildlife, alison.D.WHITMAN@odfw.oregon.gov
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
    fig_caption: yes
  #prettydoc::html_pretty:
    theme: bootstrap
    #highlight: tango

---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.pos = "!H",
  out.extra = "",
  collapse = TRUE,
  comment = "#>"
)

library(sa4ss)

dir <- "C:/Users/Jason.Cope/Documents/Github/REBS-2025/docs/Pre_assessment"

```

# 


**_Disclaimer: All data summaries and exploration presented here are preliminary and may not be indicative of the final data that will be incorporated in the 2025 assessment models_**


# Overview

The document provides a description of data available at the time of the workshop and model specifications being considered for use in the 2025 assessment of Rougheye and Blackspotted rockfishes. These two species, together, are treated as a combined species complex. Rougheye and Blackspotted rockfishes are genetically distinct, but difficult to visually distinguish, thus most data are only available for the Rougheye/Blackspotted rockfish complex, not at the species level. They range from northern California up to and throughout Alaska. They both greatly overlap in latitude and depth, and are generally considered slope rockfish, with an otogentic shift from shallower to deeper, and adults commonly found at 360 m. Rougheye seems to be proportionally more abundant when survey samples are genetically identified, and Blackspotted tend to be found, on average, deeper than Rougheye. They can school and may segregate by size and age. While we treat these species as one assessed stock from this point forward, we recognize and are mindful of the above distinctions as we conduct our analyses.


```{r child = "1_summary_of_2021_assessment.Rmd"}
```


```{r child = "2_potential_model_fleet_structure.Rmd"}
```


```{r child = "3_removals.Rmd"}
```


```{r child = "4_indices.Rmd"}
```


```{r child = "5_composition_data.Rmd"}
```


```{r child = "6_biology.Rmd"}
```





